FinalManuscript_DISCS_UG

### 2019-01-20 pcsc-paper/parts/04_inversetrig.tex
Periods and commas everywhere
added periods to equations
also some minor wording changes
Minor fixes
Plots for experiment data

\section{Inverse Trigonometric Functions}
We will now show how a Gauss--Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function. Two well-known series representations of the arctangent function exist: the Maclaurin series expansion,
\begin{align} \label{eq:arctan_maclaurin}
	\arctan x = \sum_{n=0}^{\infty}{\frac{(-1)^nx^{2n+1}}{2n+1}}, \text{ for }|x|\leq 1
\end{align}
and the following series expansion discovered by Euler in 1755, which converges more rapidly for all $x$~\cite{chien-lih_89.67_2005}.
\begin{align} \label{eq:arctan_euler}
	\arctan x = \sum_{n=0}^{\infty}
	{
	\frac
		{2^{2n}(n!)^2}
		{(2n+1)!}
	\frac
		{x^{2n+1}}
		{(1+x^2)^{n+1}}
	}
\end{align}
We will compare the quadrature approach with the method of computing partial sums from each of these series.

To obtain a Gauss--Legendre quadrature-based approximation, we take the following integral,
\begin{align*}
	\arctan x = \int_0^x{\frac{1}{1+t^2}\diff t},
\end{align*}
and perform five-point Gauss--Legendre quadrature to obtain the following closed-form approximation:
\begin{align} \label{eq:arctan_quadrature}
	\begin{split}
		&\arctan x \\
		&\approx \frac
		{4\left(225x^9 + 15925x^7 + 144753x^5 + 350595x^3 + 238140x\right)}
		{15\left(x^{10} + 480x^8 + 11760x^6 + 64120x^4 + 114660x^2 + 63504\right)}
	\end{split}
\end{align}

We note that in order to evaluate the quadrature approximation in Equation~\ref{eq:arctan_quadrature}, we must compute the value of $x^{10}$, which requires several rounds of the squaring and multiplication protocols to compute. We now compare the quadrature approximation to the partial sum composed of the first five terms of Euler's series expansion in Equation~\ref{eq:arctan_euler}, which requires a similar number of floating-point operations to compute:
\begin{align} \label{eq:arctan_euler_partial}
	\begin{split}
		&\sum_{n=0}^{4}
		{
		\frac
			{2^{2n}(n!)^2}
			{(2n+1)!}
		\frac
			{x^{2n+1}}
			{(1+x^2)^{n+1}}
		}\\
		&= \frac
		{965x^9 + 2370x^7 + 2688x^5 + 1470x^3 + 315x}
		{315\left(x^{10} + 5x^8 + 10x^6 + 10x^4 + 5x^2 + 1\right)}
	\end{split}
\end{align}

@@

To carry out the conditional check required to use these identities, a privacy-preserving comparison protocol may be used, such as in~\cite{veugen_improving_2012}.
\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=-1.25, xmax=1.25,
			ymin=1e-18, ymax=5e-5, ytickten={-18,-16,...,0},
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[thick, ACMDarkBlue] table[x=x, y=gl] {plots/abs_err_arctan.txt};
		\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Absolute error of the approximation for $\arctan x$ using quadrature approximation (Equation~\ref{eq:arctan_quadrature}) over the interval $[-1,1]$}
	\label{fig:arctan_error_2}
\end{figure}

>>>>

\section{Inverse Trigonometric Functions}
We will now show how a Gauss--Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function. Two well-known series representations of the inverse tangent function exist: the Maclaurin series expansion,
\begin{align} \label{eq:arctan_maclaurin}
	\arctan x = \sum_{n=0}^{\infty}{\frac{(-1)^nx^{2n+1}}{2n+1}}, \text{ for }|x|\leq 1,
\end{align}
and the following series expansion discovered by Euler in 1755, which converges more rapidly for all $x$~\cite{chien-lih_89.67_2005}.
\begin{align} \label{eq:arctan_euler}
	\arctan x = \sum_{n=0}^{\infty}
	{
	\frac
		{2^{2n}(n!)^2}
		{(2n+1)!}
	\frac
		{x^{2n+1}}
		{(1+x^2)^{n+1}}
	}.
\end{align}
We will compare the quadrature approach with the method of computing partial sums from each of these series.

To obtain a Gauss--Legendre quadrature-based approximation, we take the following integral,
\begin{align*}
	\arctan x = \int_0^x{\frac{1}{1+t^2}\diff t},
\end{align*}
and perform five-point Gauss--Legendre quadrature to obtain the following closed-form approximation:
\begin{align} \label{eq:arctan_quadrature}
	\begin{split}
		&\arctan x \\
		&\approx \frac
		{4\left(225x^9 + 15925x^7 + 144753x^5 + 350595x^3 + 238140x\right)}
		{15\left(x^{10} + 480x^8 + 11760x^6 + 64120x^4 + 114660x^2 + 63504\right)}.
	\end{split}
\end{align}

We note that in order to evaluate the quadrature approximation in Equation~\ref{eq:arctan_quadrature}, we must compute the value of $x^{10}$, which requires several rounds of the squaring and multiplication protocols to compute. We now compare the quadrature approximation to the partial sum composed of the first five terms of Euler's series expansion in Equation~\ref{eq:arctan_euler}, which requires a similar number of floating-point operations to compute:
\begin{align} \label{eq:arctan_euler_partial}
	\begin{split}
		&\sum_{n=0}^{4}
		{
		\frac
			{2^{2n}(n!)^2}
			{(2n+1)!}
		\frac
			{x^{2n+1}}
			{(1+x^2)^{n+1}}
		}\\
		&= \frac
		{965x^9 + 2370x^7 + 2688x^5 + 1470x^3 + 315x}
		{315\left(x^{10} + 5x^8 + 10x^6 + 10x^4 + 5x^2 + 1\right)}.
	\end{split}
\end{align}

@@

To carry out the conditional check required to use these identities, a privacy-preserving comparison protocol may be used, such as in~\cite{veugen_improving_2012}.
\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=-1, xmax=1,
			ymin=1e-18, ymax=5e-5, ytickten={-18,-16,...,0},
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[thick, ACMDarkBlue] table[x=x, y=gl] {plots/abs_err_arctan.txt};
		\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Absolute error of the approximation for $\arctan x$ using quadrature approximation (Equation~\ref{eq:arctan_quadrature}) over the interval $[-1,1]$}
	\label{fig:arctan_error_2}
\end{figure}

### 2019-01-20 pcsc-paper/parts/05_testsforaccuracy.tex
Plots for experiment data

@@

>>>>

\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=0, xmax=255,
			ymin=1e-3, ymax=1.5,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_log_errs.txt};
		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_log_errs.txt};
		\legend{Scaled quadrature, Original quadrature}
		\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Comparison of logarithm approximation errors under Paillier}
	\label{fig:comp_log}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=-1, xmax=1,
			ymin=1e-7, ymax=1,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_arctan_errs.txt};
		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_arctan_errs.txt};
		\legend{Gauss--Legendre quadrature, Partial sum of Euler's series}
		\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Comparison of inverse tangent approximation errors under Paillier}
	\label{fig:comp_arctan}
\end{figure}
